### 2012-09-01 inst/examples/figure3.Rmd
cpu settings for farm

``` {r beparallel, cache=FALSE}
require(snowfall)
sfInit(parallel=TRUE, cpu=4)
````

@@

  SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=1e3)
  opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                       profit, delta, reward=0)
}
````

@@

``` {r sethiplots, rerun=TRUE}
require(reshape2)
policy <- melt(data.frame(stock = x_grid, low=low$D[,1],
               g = g$D[,1], m = m$D[,1], i= i$D[,1]), 
               id = "stock")

ggplot(policy) + 
#  geom_point(aes(stock, stock-x_grid[value], color=variable)) +
	geom_smooth(aes(stock, stock-x_grid[value], color=variable)) +
  ylab("escapement") 
```

>>>>

``` {r beparallel, cache=FALSE}
require(snowfall)
sfInit(parallel=TRUE, cpu=16)
````

@@

  SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=1e5)
  opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                       profit, delta, reward=0)
}
````

@@

``` {r sethiplots, rerun=TRUE}
require(reshape2)
policy <- melt(data.frame(stock = x_grid, det=det$D[,1],
               g = g$D[,1], m = m$D[,1], i= i$D[,1]), 
               id = "stock")

ggplot(policy) + geom_line(aes(stock, stock-x_grid[value], color=variable))

linear <- dt[,approx(stock, stock-x_grid[value], xout=seq(1,150, length=20)), by=variable]
ggplot(linear) + geom_line(aes(x,y,color=variable))
#  geom_point(aes(stock, stock-x_grid[value], color=variable)) +
	#geom_smooth(aes(stock, stock-x_grid[value], color=variable)) 
```
